Equilivest: A Robotic Vest to aid in Post-Stroke Dynamic Balance Rehabilitation

### 2022-10-10 review/iros_original.tex
Submitted after review version.@

Patient is a 36 years-old female, without any history of chronic ailment, who suffered an acute brainstem stroke after giving birth.  The stroke was on posterior fossa subarachnoid due to a brain artereovenous malformation (AVM), which could be linked to pregnancy or puerperium~\cite{Porras.etal2017}.  Patient was in induced coma for around 1 month, and after that unable to walk, move, talk or swallow.  After two years of intensive rehabilitation, the patient managed to recover significantly, including from dysphagia, which was very important in order to remove the feeding tube allowing her to start speech recovering.

>>>>

Patient is a 36 years-old female, without any history of chronic ailment, who suffered an acute brainstem stroke after giving birth.  The stroke was on posterior fossa subarachnoid due to a brain artereovenous malformation (AVM), which could be linked to pregnancy or puerperium~\cite{Porras.etal2017}.  Patient was in induced coma for around 1 month, and after that unable to walk, move, talk or swallow.  Throughout a first period of intensive rehabilitation, the patient managed to recover significantly, including from dysphagia.
%  which was very important in order to remove the feeding tube allowing her to start speech recovering.
